---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(rpart)
library(randomForest)
library(wakefield)
library(dplyr)

A.sim <- function(matrix.pi) {
  N <- nrow(matrix.pi) # sample size
  K <- ncol(matrix.pi) # treatment options
  if (N<=1 | K<=1) stop("Sample size or treatment options are insufficient!")
  if (min(matrix.pi)<0) stop("Treatment probabilities should not be negative!")
  
  # normalize probabilities to add up to 1 and simulate treatment A for each row
  probs <- t(apply(matrix.pi,1,function(x){x/sum(x,na.rm = TRUE)}))
  A <- apply(probs, 1, function(x) sample(0:(K-1), 1, prob = x))
  return(A)
}
```

# MOTRL

<!-- badges: start -->
<!-- badges: end -->

The goal of MOTRL is to directly estimate optimal dynamic treatment regime (DTR) or tolerant DTR (tDTR) in a multi-stage multi-treatment setting. The users can self-define their preference on different priorities and the tolerant rate at each stage.

## Installation

You can install the development version of MOTRL from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("SelinaSong0412/MOTRL")
```

## Example

See below for two examples of using MOTRL to estimating tolerant DTR.

```{r example}
library(MOTRL)
```

**(a). Bi-objective scenario: one stage, three treatments**

Here we simulate some data of 1000 observeations for 6 variables. 
The weights on the two objective are set as (0.7, 0.3). 

```{r}
# Simulate 6 covariates
set.seed(300)
N = 1000
x1<-rnorm(N) # each covariates follows N(0,1)
x2<-rnorm(N)
x3<-rnorm(N)
x4<-rnorm(N)
x5<-rnorm(N)
x6<-answer(N, x = c("No", "Yes"), name = "Smoke")
X0<-cbind(x1,x2,x3,x4,x5,x6) # All of the covariates

# Simulate observed treatment and optimal treatment  
# observed treatment (A1) with total possible number of treatment = 3
pi10 <- rep(1, N)
pi11 <- exp(0.5*x4 + 0.5*x1)
pi12 <- exp(0.5*x5 - 0.5*x1)
# weights matrix
matrix.pi1 <- cbind(pi10, pi11, pi12)
A1 <- A.sim(matrix.pi1)
class.A1 <- sort(unique(A1))
# propensity stage 1
pis1.hat <- M.propen(A1, cbind(x1,x4,x5))
g1.opt <- (x2 <= 0.5)*(x1 > 0.5) + 2*(x2 > 0.5)*(x1 > -1)

# outcome 1
Y11 <- exp(1.68 + 0.2*x4 - abs(0.5*x1 - 1)*((A1 - g1.opt)^2)) - 3*(A1 == 1) + rnorm(N,0,1)
# outcome 2 
Y12 <- 2.37 + x4 + 2*x5 + 2*(A1 == 0)*(2*(g1.opt == 0) - 1) + 1.5*(A1 == 2)*(2*(g1.opt == 2) -1) + 1.5*(exp((A1 == 1)) -1) + rnorm(N,0,1)
Ys1 = cbind(Y11, Y12)
```

Then, we start to grow the DTR tree and the 60% tolerant DTR tree:
```{r}
w0 = 0.7         # set the weight on the first objective as 0.7
wt = c(w0, 1-w0) # the weight vector is (0.7, 0.3)
MOTRL0 = MO.tol.DTRtree(Ys1, w = wt, A1, H=X0, delta = 0, pis.hat=pis1.hat, lambda.pct=0.05, minsplit=max(0.05*N,20),depth = 3)
MOTRL0$tree      # return the MOTRL tree with zero tolerance (only the optimal treatment provided) 

MOTRL1 = MO.tol.DTRtree(Ys1, w = wt, A1, H=X0, delta = 0.4, pis.hat=pis1.hat, lambda.pct=0.05, minsplit=max(0.05*N,20),depth = 3)
MOTRL1$tree      # return the 60% tolerant DTR tree

# Run this to get the pseudo outcomes:
# MOTRL1$POs
# Run this to get the loss on pseudo outcome, which is used when generate the DTR tree for the previous stage:
# MOTRL1$PO.loss
```

**(b). Bi-objective scenario: two stages, three treatments**

Using the above simulated data as stage 1 data, we continue simulate a stage two data: 
```{r}
# observed stage 2 treatment, A2, with K2 = 3
pi20 <- rep(1,N)
pi21 <- exp(0.2*Y12 - 0.5)
pi22 <- exp(0.2*Y11 - 0.5*x2)
matrix.pi2 <- cbind(pi20, pi21, pi22)
A2 <- A.sim(matrix.pi2)
class.A2 <- sort(unique(A2))
# propensity stage 2
pis2.hat<-M.propen(A2,cbind(Y11,Y12,x2))
# optimal stage 2 treatment
g2.opt <- (x1 <= 0)*((x5 > -0.5) + (x5 > 1.5)) + 2*(x1 > 0)*(x3 > - 1)
  
### stage 2 outcome 1 
Y21 <- 1 + exp(1.5 + 0.2*x2 - abs(1.5*x3 + 2)*(A2 - g2.opt)^2) - 2*(A2 == 1) + rnorm(N,0,1)
### stage 2 outcome 2 
Y22 <- 1.7 + x2 + 2*(A2 == 0)*(2*(g2.opt == 0) - 1) + (A2 == 1)*(2*(g2.opt == 1) - 1) +
  3*(A2 == 2)*(2*(g2.opt == 2) - 1) + 1.2*(exp((A2 == 1)) -1) + rnorm(N,0,1)
Ys2 = cbind(Y21, Y22)
```

We start the estimation from the second stage. Same weight vector (0.7, 0.3) is applied.
```{r}
# Stage 2 estimation by backward induction
w21 = c(w0, 1-w0) # same weights 
MOTRL20 = MO.tol.DTRtree(Ys2, w = w21, A2, H=cbind(X0,A1,Ys1), delta = 0, pis.hat=pis1.hat, 
                         lambda.pct=0.05, minsplit=max(0.05*N,20),depth = 3)
MOTRLtree20 = MOTRL20$tree
MOTRLtree20

MOTRL21 <- MO.tol.DTRtree(Ys2, w = w21, A2, H=cbind(X0,A1,Ys1), delta = 0.4, pis.hat=pis1.hat, 
                          lambda.pct=0.05, minsplit=max(0.05*N,20),depth = 3)
MOTRLtree21 = MOTRL21$tree
MOTRLtree21
```
  
Then, calculate the accumulated mean pseudo outcomes, and use it as the outcomes (`Ys`).
```{r}
# calculate average pseudo outcome 
g2.MOTRLtree20 = predict_tol.DTR(MOTRLtree20, newdata = cbind(X0,A1,Ys1))
g2.MOTRLtree21 = predict_tol.DTR(MOTRLtree21, newdata = cbind(X0,A1,Ys1))
PO.MOTRL20 = Ys1 + MOTRL20$PO.loss
PO.MOTRL21 = Ys1 + MOTRL21$PO.loss

w11 = w21
MOTRL10 = MO.tol.DTRtree(PO.MOTRL20, w = w11, A1, H=X0, delta = 0, pis.hat=pis1.hat, 
                         lambda.pct=0.05, minsplit=max(0.05*N,20),depth = 3)
MOTRL10$tree
MOTRL11 <- MO.tol.DTRtree(PO.MOTRL21, w = w11, A1, H=X0, delta = 0.4,pis.hat=pis1.hat, 
                            lambda.pct=0.05, minsplit=max(0.05*N,20),depth = 3)
MOTRL11$tree
```

**(c). Tri-objective scenario: one stage, three treatments**

```{r}
N<-1000 # sample size of training data
N2<-1000 # sample size of test data
iter <- 5 # replication
w1 = 0.35
w2 = 0.35
w3 = 1 - w1 - w2

# Simulation begin
set.seed(300)
x1<-rnorm(N)              # each covariates follows N(0,1)
x2<-rnorm(N)
x3<-rnorm(N)
x4<-rnorm(N)
x5<-rnorm(N)
x6<-rnorm(N)              # each covariates follows N(0,1)
x7<-rnorm(N)
x8<-rnorm(N)
x9<-rnorm(N)
x10<-answer(N, x = c("No", "Yes"), name = "Smoke")
  
X0<-cbind(x1,x2,x3,x4,x5,x6,x7,x8,x9,x10) # All of the covariates

############### stage 1 data simulation ##############
# simulate A1, true stage 1 treatment with K1=3
pi10 <- rep(1, N)
pi11 <- exp(0.5*x4 + 0.5*x1 + 0.05*x3)
pi12 <- exp(0.5*x5 - 0.5*x1 + 0.5*x2)
  
# weights matrix
matrix.pi1 <- cbind(pi10, pi11, pi12)
A1 <- A.sim(matrix.pi1)
class.A1 <- sort(unique(A1))
# propensity stage 1
pis1.hat <- M.propen(A1, cbind(x1,x2, x3,x4,x5))
  
# g1.opt <- (x2 <= 0.5)*(x1 > 0.5) + 2*(x2 > 0.5)*(x1 > -1)
# change !
g1.opt <- (x1 <= 0.5)*(x2 > -0.2) + (x1 > 0.5)*2*(1 - (x3 > -1)*(x3 < -0.5))
  
# outcome 1
Y11 <- 0.57 + exp(1.67 + 0.2*x6 - abs(1.5*x7 + x4 - 1)*((A1 - g1.opt)^2)) - 
    3*(A1 == 1) + rnorm(N,0,1) # noise on A = 1 and 2
# outcome 2
Y12 <- 1.9 + x5 + 0.5*x6 + 2*(A1 == 0)*(2*(g1.opt == 0) - 1) + 1.5*(A1 == 2)*(2*(g1.opt == 2) -1) + 0.5*(A1 == 1)*(2*(g1.opt == 1) -1) +
    1.8*(exp((A1 == 1)) -1) + rnorm(N,0,1) # noise on A = 1 and 2
# outcome 3
Y13 <- 5.32 + x8 - exp(0.1 + 2*(x10 == "No"))*(1*(A1 == 1) + 0.5*(A1 == 0) + 0.1*(A1 == 2)) + rnorm(N,0,1) # noise on A = 1 and 2
  
# stage 1 outcome
Ys1 = cbind(Y11, Y12, Y13)


# MODTRtree and average potential outcome for each of the three objectives (with tolerant rate 100%, 60%)
wt = c(w1, w2, w3)
MOTRL0 = MO.tol.DTRtree(Ys1, w = wt, A1, H=X0, delta = 0, pis.hat=pis1.hat, lambda.pct=0.02, minsplit=20,depth = 4)
MOTRL0$tree
MOTRL1 <- MO.tol.DTRtree(Ys1, w = wt, A1, H=X0, delta = 0.4,pis.hat=pis1.hat, lambda.pct=0.02, minsplit=20,depth = 4)
MOTRL1$tree
```







